RNA-seq from 4 cell populations

### 2021-07-28 deconvolution/fans4/molec_profiling.Rmd
bug fix

### Esimate precision weights
```{r voom}
form = ~ (1|CellType) + (1|Individual.ID) + (1|Gender) + (1|Batch)
vobj = voomWithDreamWeights(dge, form, info, plot=TRUE, save.plot=TRUE, BPPARAM=SnowParam(36, progressbar=TRUE))
```

@@

### variancePartition
```{r vp}
form = ~ (1|CellType) + (1|Dx) + (1|CellType:Dx) + (1|Individual.ID) + (1|Gender) + (1|Batch)
vp = fitExtractVarPartModel( geneExpr, form, info, BPPARAM=SnowParam(36, progressbar=TRUE))

@@

  form = ~ CellType + Gender
  fit = dream( vobj, form, infoSub, BPPARAM=SnowParam(6, progressbar=TRUE))
  fit = eBayes(fit)

>>>>

### Esimate precision weights
```{r voom}
form = ~ (1|CellType) + (1|Individual.ID) + (1|Gender) + (1|Batch)
vobj = voomWithDreamWeights(dge, form, info, plot=TRUE, save.plot=TRUE, BPPARAM=SnowParam(12, progressbar=TRUE))
```

@@

### variancePartition
```{r vp}
form = ~ (1|CellType) + (1|Dx) + (1|CellType:Dx) + (1|Individual.ID) + (1|Gender) + (1|Batch)
vp = fitExtractVarPartModel( geneExpr, form, info, BPPARAM=SnowParam(12, progressbar=TRUE))

@@

  form = ~ CellType + Gender
  vobj = voomWithDreamWeights(dge, form, infoSub, plot=FALSE, save.plot=TRUE, BPPARAM=SnowParam(12, progressbar=TRUE))

  form = ~ CellType + Gender
  fit = dream( vobj, form, infoSub, BPPARAM=SnowParam(12, progressbar=TRUE))
  fit = eBayes(fit)
